Hydrophobicity

### 2020-04-20 hydrophobicity/hydrophobicity.Rmd
Work on hydrophobicity

>>>>

```{r}
library(bbbq)
library(testthat)
```

```{r}
proteome_filename <- system.file(
  "extdata", 
  "UP000001584_83332_0.fasta", 
  package = "bbbq")
stopifnot(file.exists(proteome_filename))
```

```{r}
proteome <- ape::read.FASTA(proteome_filename, type = "AA")
```
```{r}
library(ape)
first_protein <- as.character(proteome)[[1]]
first_polypeptide <- paste0(first_protein[1:13], collapse = "")
cat(first_polypeptide)
```

```{r}
first_hydropbobicity <- Peptides::hydrophobicity(first_polypeptide)
cat(first_hydropbobicity)
```
